### 2022-05-30 article.tex
Fix ref
EOD

@@

For science to be reproducible (a fundamental property of the scientific 
method), it is the code that should be published, instead of the
English description of what the code does (i.e. the article), if one
would have to pick one, as it is the code does the actual work.
Hence, from a knowledge management perspective, emphasis should be
put more on the preservation of code, as it is the most important actor
in an experiment.

To quote a review on reproducibility \cite{peng2021reproducible}, 
'Reproducibility is typically thwarted by a 
lack of availability of the original data and computer code'.
In the case of genetic epidemiology, it is a given that the original
data cannot be published as this data is sensitive.

@@

It is the paper that accompanies the code,
as it is the code that generates the results.
When humans are fallible and code gets bigger, the likelihood of
a mismatch between the English paper and the code increases.
But regardless of the size of the code, 
it is the code that is the ground truth.

@@

There are multiple websites for hosting code, with GitHub,
and GitLab being the most well-known.
GitHub is the most commonly used website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
The use of code hosting websites, such as GitHub,
accommodates collaboration (\cite{perez2016ten}).
\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. Code coverage
correlates with code quality (\cite{horgan1994,del1995correlation}).

>>>>

\paragraph{Science should be reproducible}

A scientific claim must be reproducible before it is accepted
by the scientific community.
Reproducibility (i.e. to reproduce the same results) 
and replicability (i.e. to reconclude a conclusion)
are fundamental characteristics of scientific studies (\cite{patil2019visual}).
For computational science, it is relatively easy to 
reproduce an experiment, as all it takes is a computer, electricity,
an optional internet connection, the code and the data.
In computational science, however, it appears that 
culture to reproduce results has been lost 
and to counter this, it has been suggested to make
reproducible research a minimal requirement for 
publication (\cite{peng2011reproducible}).

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{peng2011reproducible_fig_1.png}
  \caption{
    Levels of reproducibility, from \cite{peng2011reproducible}
  }
  \label{fig:peng2011reproducible}
\end{figure}

The code of a computational experiment must be published
for an experiment to reproducible.
It is however (too) common that the original data
and/or code are unavailable (\cite{peng2021reproducible}).
One sad example is described in \cite{haibe2020importance}, where
an algorithm that detects breast cancer better than a human expert,
was irreproducible.
In the case of genetic epidemiology, it is a given that the original
data cannot be published as this data is sensitive.
The code of a computational experiment, however, can be
distributed without such problems.
It is, however, not code that is published, but an English
description of what that code does instead.
From a knowledge management's perspective,
to conserve an experiment,
it is the code that must be archived and not the
English description of what it does:
it is the code does the actual work.
Hence, from a knowledge management perspective, emphasis should be
put more on the preservation of code, as it is the most important actor
in an experiment.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a_zoom.png}
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a.png}
  \caption{
    A published off-by-one error.
    Left: a zoom in. 
    Horizontal axis is the sample name.
    Vertical axis is UNKNOWN.
    Color in the cell denotes gene expression.
    The colors above the cells, with the dendrogram, shows
    red for non-responders (red) and responsive (blue).
    Right: visisualization of sample that shows samples are duplicated,
    as annotated by the pink rectangles. Note that, due to this, some
    samples are both non-responders and responders.
    Adapted from \cite{baggerly2009deriving}
  }
  \label{fig:baggerly2009deriving}
\end{figure}

It is the paper that accompanies the code,
as it is the code that generates the results.
When humans are fallible and code gets bigger, the likelihood of
a mismatch between the English paper and the code increases.
We know that the most common errors are 
simple (and may legitimately fear that those simple errors are common) 
(\cite{baggerly2009deriving}),
and this example is not too far off from the
examples given in that paper.

But regardless of the size of the code, 
it is the code that is the ground truth.

@@

There are multiple websites for hosting code, with BitBucket, GitHub,
GitLab and SourceForge being the most well-known.
Of these, GitHub is the most popular website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
The use of code hosting websites, such as GitHub,
accommodates collaboration (\cite{perez2016ten}).
\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

\paragraph{Code coverage helps assess code quality}

A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. Code coverage
correlates with code quality (\cite{horgan1994,del1995correlation}). 
The non-profit organisation rOpenSci, which peer-reviews code,
has made it a prerequisite to have a code coverage of 100\%.
